%-------------------------
% Resume in LateX
% Template Author : Sourabh Bajaj
% Resume Author: Ariel Perez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Ariel Perez}} & Email: \href{mailto:arielperezch@gmail.com}{arielperezch@gmail.com}\\
  \faLinkedinSquare \, \href{https://linkedin.com/ariel-perez-ch}{ariel-perez-ch} & Mobile: \href{tel:+12066984457}{+1-206-698-4457} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Luminai}{San Mateo, CA}
      {Principal Machine Learning Engineer}{Mar 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Browser automation execution engine}
          {Designed and built the automation execution engine in async python with a focus on creating an amenable setup for code generation and planning.}
        \resumeItem{AI code generation}
          {Designed and built a code generation system for Playwright-based browser automations with human in the loop. This includes multiple stages of automatic validation, evaluation pipelines and automatic prompt optimization running in multiple containers using DSPy.}
        \resumeItem{AI plan generation}
          {Experimented with and built several versions of AI driven plan generation for browser automations: One-shot, incrementally and interactively as part of a run, and from recordings.}
        \resumeItem{Question answering with RAG support}
          {Designed and built a configurable question answering integration as a standalone application on Kubernetes. The integration could be set up and accessed from the execution engine and potentially make use of ephemeral vector storage databases using Qdrant and DSPy.}
        \resumeItem{Automated contract parsing for medical underpayments}
          {Designed the initial version of an automated system for parsing out provider-insurance contracts into a deterministic claim processing system that can calculate the proper payments. }
      \resumeItemListEnd

    \resumeSubheading
      {Cruise}{San Francisco, CA}
      {Senior Machine Learning Engineer -- Prediction}{Mar 2021 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Led last-mile effort in reaching model parity after a TensorFlow $\rightarrow$ PyTorch migration}
          {Designed a plan for adding component-level tests on both models and feed them the same input to spot discrepancies. Worked hands-on with two staff engineers from the infrastructure team, leading the investigation and resolution of issues as they were found.}
        \resumeItem{Various improvements in vehicle trajectory prediction}
          {Reduced infeasible predictions by  adding a new loss function. Implemented a two stage prediction for vehicle trajectories.}
        \resumeItem{Various improvements in self-trajectory planning}
          {Increased the AV caution when in situations involving Emergency Vehicles. Improved data quality and ground truth selection in training data.}
        \resumeItem{Developer productivity}
          {Built an experiment manager as a git-like command line utility to more easily aggregate experiments from different branches. Set up easy dashboard generator with generated SQL and LookML.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{Mountain View, CA}
      {Software Engineer - Image Search Ranking}{Sep 2018 - Feb 2021}
      \resumeItemListStart
        \resumeItem{Commercial query ranking}
          {Led work to develop a new inspirational image classifier and deployed initial version to production. Improved result quality by boosting more reputable sites.}
        \resumeItem{ML Fairness}
          {Enabled ML fairness prioritization and subsequent work by building a tool to identify sources of bias within the ranking stack.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon - Seller Insights}{Seattle, WA}
      {Software Development Engineer}{May 2017 -- Aug 2018}
      \resumeItemListStart
        \resumeItem{Functionality for ML pipelines}
          {Added support for deploying ML workloads with an additional \emph{.jar} file to support more complex projects in collaboration with the infra team in Detroit. Set up a build process to deploy changes to the production environment. Built utility to version model artifacts along with the required pre-processors.}
      \resumeItemListEnd

    \resumeSubheading
      {Foris}{Santiago, Chile}
      {Data Scientist / Full-Stack Software Engineer}{Sep 2015 - May 2017}
      \resumeItemListStart
        \resumeItem{NLP for analysis of open-ended answers in surveys}
          {Designed and built system including data cleanup, classification into pre-defined categories, and presentation of the results. Classification was performed using an RNN on top of word2vec embeddings in TensorFlow.}
        \resumeItem{Optimization for timetabling problem in higher-education institutions}
          {Developed real-time search algorithms for providing time-bounded heuristic solutions to a subproblem of the timetabling problem. Used \emph{reductions} (computational complexity) to adapt the solution to diverse institutions without modifying the core algorithm.}
          
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pontificia Universidad Catolica de Chile}{Santiago, Chile}
      {Professional engineer degree in computer science - Summa cum laude}{Mar 2010 -- Jul 2015}
    \resumeSubheading
      {MOOCs (Coursera / Udacity)}{Online}
      {Machine Learning, Algorithms on Strings, RL, AI nano-degree, Advanced ML on Google Cloud}{2011 - Present}
  \resumeSubHeadingListEnd


%-----------TEACHING--------------  
\section{Teaching}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pontificia Universidad Catolica de Chile}{Santiago, Chile}
      {Undergraduate teaching assistant}{2011 - 2015}
      \resumeItemListStart
        \resumeItem{Introduction to Programming, Advanced Programming, Logic for Computer Science}
          {Gave complementary lectures, designing homework assignments and grading coursework.}
        \resumeItem{Linear Algebra, Optimization}
          {Graded coursework}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Side Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Blog on computational neuroscience}
      {\href{https://arielos.substack.com}{arielos.substack.com}}
    \resumeSubItem{\href{https://github.com/asparagus/jigsaw-ml}{jigsaw-ml} (2023)}
      {Interoperable ML blocks for modular building of high complexity models.}
    \resumeSubItem{\href{https://github.com/asparagus/dota-draft}{dota-draft} (2023)}
      {ML project for suggestion of heroes during the draft phase of DOTA, a game I used to play often. The project scrapes data from an API, stores and processes the data on Google Cloud Platform and trains PyTorch models to predict the win \% of a given draft.}
    \resumeSubItem{\href{https://github.com/asparagus/playground}{playground} (2020)}
      {Practice ground for implementation and benchmark of different ML architectures on a variety of standardized datasets.}
    \resumeSubItem{\href{https://github.com/asparagus/hopfield}{hopfield} (2020)}
      {Experiments with Hopfield networks}
    \resumeSubItem{\href{https://github.com/asparagus/protobrain}{protobrain} (2019)}
      {Library inspired by Numenta's NuPIC for neural inspired computation}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, SQL, JavaScript, others}
      \hfill
      \textbf{Technologies}{: DSPy, PyTorch, TF, Qdrant, W\&B, GCP}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
